Convergence rate of MAP estimates \\ for the exponential family

### 2021-02-23 main.tex
Clean alternative tracks

This article \url{http://davidpfau.com/assets/generalized_bvd_proof.pdf} gives a bias variance decomposition which applies here. However it does not give interesting conclusions.

@@

\section{Alternative Research Track}
Weakly supervised : missing part of $x_i$ for each $i$.

Structured prediction : graphical model on $X$.

\section{Related Work}
Exponential families are a mainstream tool in machine learning. They are used  to generalize linear regression \citep{mccullagh1989generalized}, PCA \citep{collins2001generalization} or k-means \citep{banerjee2005clustering} to diverse data types and distributions.
\citet[Chapter 3]{wainwright2008graphical} give a great overview of exponential families and their dual structure. 
\citet{agarwal2010geometric} highlight that the MAP problem of exponential families is also a Bregman median problem. They then use this equivalence to justify the use of conjugate prior in Bayesian estimation and hybrid generative-discriminative modeling.
Note that this equivalence holds only if sufficient statistics are within $\dom \conj  = \mathrm{Im} (\nabla\logpart)$, a point ignored by authors yet critical as it does not hold for multivariate normals with unknown covariance. 
\citet{raskutti2015information} highlight the equivalence between mirror descent in $\natp$ and natural gradient descent in $\meanp$ (or vice-versa) for the exponential family. Then they use the optimality result by Shunichi Amari on Natural Gradient Descent to show that Mirror Descent iterates reach the Cramer-Rao lower bound.
\citet{kunstner2020homeomorphic} show with an exquisite elegance that Expectation-Maximization in exponential families can be cast as mirror descent on the negative log-likelihood. Then they use recent mirror descent rates based on the idea of relative smoothness \citep{birnbaum2011distributed, bauschke2017descent, lu2018relatively} to show convergence of EM in KL-divergence, including for the ubiquitous Gaussian Mixture model, which had resisted bounding attempts for 50 years.

>>>>

@@

\section{Related Work}
Exponential families are a mainstream tool in machine learning. They are used  to generalize linear regression \citep{mccullagh1989generalized}, PCA \citep{collins2001generalization} or k-means \citep{banerjee2005clustering} to diverse data types and distributions.
\citet[Chapter 3]{wainwright2008graphical} give a great overview of exponential families and their dual structure.

\citet{agarwal2010geometric} highlight that the MAP problem of exponential families is also a Bregman median problem. They then use this equivalence to justify the use of conjugate prior in Bayesian estimation and hybrid generative-discriminative modeling.
Note that this equivalence holds only if sufficient statistics are within $\dom \conj  = \mathrm{Im} (\nabla\logpart)$, a point ignored by authors yet critical as it does not hold for multivariate normals with unknown covariance. 
\citet{raskutti2015information} highlight the equivalence between mirror descent in $\natp$ and natural gradient descent in $\meanp$ (or vice-versa) for the exponential family. Then they use the optimality result by Shunichi Amari on Natural Gradient Descent to show that Mirror Descent iterates reach the Cramer-Rao lower bound.

\citet{kunstner2020homeomorphic} show with an exquisite elegance that Expectation-Maximization in exponential families can be cast as mirror descent on the negative log-likelihood. Then they use recent mirror descent rates based on the idea of relative smoothness \citep{birnbaum2011distributed, bauschke2017descent, lu2018relatively} to show convergence of EM in KL-divergence, including for the ubiquitous Gaussian Mixture model, which had resisted bounding attempts for 50 years.

\citet{pfau2013generalized} gives a bias variance decomposition for Bregman divergences. However it does not give interesting conclusions for our problem of interest.

\subsection{Alternative Research Tracks}
\begin{itemize}
	\item Weakly supervised : missing part of $x_i$ for each $i$.
	\item Structured prediction : graphical model on $X$ or other kind of structure.
\end{itemize}
